Submission HW1

### 2022-08-31 hw1-1/submission.Rmd
final knot for submission

```{r}
#lib imports
library(cowplot)
library(ggplot2)
library(reshape2)
library(kknn)
```

@@

```{r}
# Rectangular(unweighted) kernel as optimised 
knn_pred <- vector(mode="list",length = dim(knn_data)[1])
pred_table <- data.frame(k_val=numeric(0),acc_val=double(0)) #dataframe to hold accuracy with k
for (k0 in seq(1,nrow(knn_data),by=25)){ #To loop over k values
  for (i in 1:nrow(knn_data)){ #To loop over indvidual data points
    knn_model_v0<-kknn(R1~.,train = knn_data[-i,],test = knn_data[i,],k=k0,kernel="rectangular",scale = TRUE)
    knn_pred[i]<-as.integer(round(fitted(knn_model_v0),digits = 0)==knn_data$R1[i]) #majority voting > 0.5
  }
  percent_accuracy<-round(as.double(sum(unlist(knn_pred)))/nrow(knn_data),digits =2)
  pred_table[nrow(pred_table)+1,]=c(k0,percent_accuracy)
}
plot(pred_table)
```

@@

>>>>

```{r}
#lib imports
library(cowplot)
library(ggplot2)
library(reshape2)
library(kknn)
library(pROC)
```

@@

```{r}
# Rectangular(unweighted) kernel as optimised 
knn_pred <- vector(mode="list",length = dim(org_cc_data)[1])
pred_table <- data.frame(k_val=numeric(0),acc_val=double(0)) #dataframe to hold accuracy with k
for (k0 in seq(1,nrow(org_cc_data),by=25)){ #To loop over k values
  for (i in 1:nrow(org_cc_data)){ #To loop over indvidual data points
    knn_model_v0<-kknn(R1~.,train = org_cc_data[-i,],test = org_cc_data[i,],k=k0,kernel="rectangular",scale = TRUE)
    knn_pred[i]<-as.integer(round(fitted(knn_model_v0),digits = 0)==org_cc_data$R1[i]) #majority voting > 0.5
  }
  percent_accuracy<-round(as.double(sum(unlist(knn_pred)))/nrow(org_cc_data),digits =2)
  pred_table[nrow(pred_table)+1,]=c(k0,percent_accuracy)
}
plot(pred_table)
```

@@

```{r, include=FALSE}
# Threshold Function
f0<-function(x,t=t0){
  ifelse(x>t,1,0)
}
```

```{r, include=FALSE}
# Accuracy Function
accuracy_knn <- function(df){
  acc_overall = sum(df$act_class == df$pred_class)/nrow(df)
  df_1 = df[df$act_class > 0,]
  df_0 = df[df$act_class == 0,]
  acc_1 = sum(df_1$act_class == df_1$pred_class)/nrow(df_1)
  acc_0 = sum(df_0$act_class == df_0$pred_class)/nrow(df_0)
  return (c(acc_overall, acc_1, acc_0))
}
```

```{r, include=FALSE}
# Data frame for storing values
threshold_auc<-data.frame(k=double(0), threshold_val=double(0), auc_val=double(0), acc_overall=double(0), acc_1=double(0), acc_0=double(0))

# Loop iterating over values of K for finding best value
for(k in seq(20, 50, by=5)){
  test_pred<-data.frame(pred_val=double(0),act_class=numeric(0))
  for (i in 1:nrow(org_cc_data)){
      knn_model_v1<-kknn(R1~., train = org_cc_data[-i,], test = org_cc_data[i,], k=k, kernel="rectangular", scale = TRUE)
      knn_pred[i]<-as.double(fitted(knn_model_v1))
      test_pred[nrow(test_pred)+1,]=c(knn_pred[i],org_cc_data$R1[i])
  }

  # Iteration over values of threshold to determine the threshold which maximizes AUC score and hence the better separation between the two classes
  for(t0 in seq(0.2,0.8,by=0.02)){
    test_pred$pred_class<-apply(data.frame(test_pred$pred_val),1,f0)
    auc_val<-auc(test_pred$act_class,test_pred$pred_class)
    print(auc_val)
    print(c(k, t0, auc_val, accuracy_knn(test_pred)))
    threshold_auc[nrow(threshold_auc)+1,]=c(k, t0,auc_val,accuracy_knn(test_pred)[1], accuracy_knn(test_pred)[2], accuracy_knn(test_pred)[3])
  }
}
```

```{r}
threshold_auc
```

```{r}
# Final step to determine the highest value of AUC for every K
final_frame<-data.frame(k=double(0), threshold_val=double(0), auc_val=double(0), acc_overall=double(0), acc_1=double(0), acc_0=double(0))
for(k_i in seq(20, 50, by=5)){
  print(k_i)
  data_i = threshold_auc[threshold_auc$k == k_i,]
  print (data_i[which.max(data_i$auc_val),])
  final_frame[nrow(final_frame)+1, ] <- data_i[which.max(data_i$auc_val),]
}
```

```{r}
final_frame
```
